\section{List of publications}
  \begin{etaremune}  %add \usepackage{etaremune}
  \item Linking the Sampling Frequency with Multiscale Entropy to classify mitoBK patch-clamp data, L. Machura, A. Wawrzkiewicz-Jałowieckaa, P. Bednarczyk, and P. Trybek, Biomed Signal Process Control (2022)
, 
\item Dynamical Diversity of Mitochondrial BK Channels Located in Different Cell Types, A. Wawrzkiewicz-Jałowieckaa, P. Trybek, L. Machura and P. Bednarczyk, BioSystems 199,  104310 (2021) 

\item Multifractal Properties of BK Channels’ Currents in Human Glioblastoma Cells, A. Wawrzkiewicz-Jałowiecka, P. Trybek, B. Dworakowska and L. Machura, J. Phys. Chem. B 124,  12  2382-2391  (2020)

\item Differences in Gating Dynamics of BK Channels in Cellular and Mitochondrial Membranes from Human Glioblastoma Cells Unraveled by Short- and Long-Range Correlations Analysis, A. Wawrzkiewicz-Jałowiecka, P. Trybek, P. Borys, B. Dworakowska, L. Machura and P. Bednarczyk, Cells 9,  2305 (2020)

\item The distribution of information for sEMG signals in the rectal cancer treatment process, P. Trybek, M. Nowakowski, J. Salowka and L. Machura, BioSystems 176,  13 (2019)

\item Upper extremity surface electromyography signal changes after laparoscopic training, M. Nowakowski, P. Trybek, M. Rubinkiewicz, T. Cegielny, M. Romaniszyn, M. Pędziwiatr, L. Machura, Videosurgery Miniinv,  (2018)  doi:10.5114/wiitm.2018.78744

\item Single measurement detection of individual cell ionic oscillations using an n-type semiconductor – electrolyte interface, M. Pietruszka, M. Olszewska, L. Machura and E. Rowinski, Sci. Rep. 8,  7875 (2018)

\item Inter-pulse intervals of external anal sphincter surface EMG signals recorded from colorectal cancer patients, L. Machura, P. Trybek, J. Salowka and M. Nowakowski, submitted (2018)
, 
\item Multifractal characteristics of external anal sphincter based on sEMG signals, P. Trybek, M. Nowakowski and L. Machura, Med Eng Phys 55,  9 (2018)

\item Mechanosensitivity of the BK channels in human glioblastoma cells - kinetics and dynamical complexity, A. Wawrzkiewicz-Jalowiecka, P. Trybek, L. Machura, B. Dworakowska, Z. J. Grzywna, J Membrane Biol,  1-13 (2018)

\item  Sample entropy of sEMG signals at different stages of rectal cancer treatment, P. Trybek, M. Nowakowski, J. Salowka, J. Spiechowicz, L. Machura, Entropy 20,  863 (2018)

\item Sensitivity and specificity of multichannel surface electromyography in diagnosing fecal incontinence, M. Nowakowski, K. A. Tomaszewski, P. Trybek, L. Machura, R. M. Herman, Folia Med Cracov. LVII 1,  29 (2017)

\item Correlation based analysis of sEMG signals during complex muscle activity. Feasibility study of new methodology., M. Nowakowski, P. Trybek and L. Machura, Folia Med Cracov. LVII 2,  41 (2017)

\item Efficiency of transport in periodic potentials: dichotomous noise contra deterministic force, J. Spiechowicz,  J. Luczka and L. Machura, J. Stat. Mech.,  054038 (2016)

\item Evaluation of the training objectives with surface electromyography, P. Trybek, M. Nowakowski and L. Machura, Bio-Algorithms and Med-Systems 12,  25 (2016)

\item Persistent currents in metallic rings containing a quantum dot, L. Machura and J. Luczka, Phys. Lett. A 379,  1654 (2015)

\item GPU accelerated Monte Carlo simulation of Brownian motors dynamics with CUDA, J. Spiechowicz, M. Kostur and L. Machura, Comput. Phys. Commun. 191,  140 (2015)

\item Directed transport in coupled noisy Josephson junctions controlled via ac signals, L. Machura, J. Spiechowicz and J. Luczka, Phys. Scr. 151,  014021 (2012) 

\item Two coupled Josephson junctions: dc voltage controlled by biharmonic current, L. Machura, J. Spiechowicz, M. Kostur and J. Łuczka, J. Phys. Condens. Matter 24,  085702 (2012)

\item Control of transport characteristics in two coupled Josephson junctions, J. Spiechowicz, L. Machura, M. Kostur and J. Łuczka, Acta Phys. Polon. B 43,  1203 (2012) 

\item Transport driven by biharmonic forces: impact of correlated thermal noise, Ł. Machura and J. Łuczka, Phys. Rev. E 82,  031133 (2010)

\item Negative conductances of Josephson junctions: Voltage fluctuations and energetics, Ł. Machura, M. Kostur, P. Talkner, P. Hänggi, and J. Łuczka, Phys. E 42,  590 (2010)

\item Current-flux characteristics in mesoscopic nonsuperconducting rings, Ł. Machura, S. Rogoziński, and J. Łuczka, Fast Track J. Phys.: Condens. Matter 22,  422201 (2010)

\item Current characteristics of mesoscopic rings in quantum Smoluchowski regime, S. Rogoziński, Ł. Machura and J. Łuczka, Eur. Phys. J. - Special Topics 187,  5 (2010) 

\item Inertial Brownian motors driven by biharmonic signals, Ł. Machura, M. Kostur, and J. Łuczka, Chemical Physics 375,  445 (2010)

\item Transmission of magnetic signals in noisy mesorings, L. Machura, J. Dajka and J. Łuczka, J. Stat. Mech.,  P01030 (2009)

\item Anomalous transport in biased ac-driven Josephson junctions: Negative conductances, M. Kostur, L. Machura, P. Talkner, P. Hänggi, and J. Łuczka, Phys. Rev. B 77,  104509 (2008) 

\item Mesoscopic rings: multi-states induced by quantum thermal fluctuations, J. Dajka, L. Machura, S. Rogoziński and J. Łuczka, Materials Science Poland 26,  871 (2008)

\item Transport Characteristics of Molecular Motors, L. Machura, M. Kostur and J. Łuczka, biosystems 05,  033 (2008)

\item Negative Conductance in Driven Josephson Junctions, M. Kostur, Ł. Machura, J. Łuczka, P. Talkner, P. Hänggi, Acta Physica Polonica B 39,  1115 (2008)

\item Absolute negative mobility induced by thermal equilibrium fluctuations, L. Machura, M. Kostur, P. Talkner, J. Luczka and P. Hänggi, Phys. Rev. Lett. 98,  040601 (2007)

\item Magnetic flux in mesoscopic rings: Quantum Smoluchowski regime, J. Dajka, Ł. Machura, S. Rogoziński, and J. Łuczka, Phys. Rev. B 76,  045337 (2007)

\item Flux-biased mesoscopic rings, J. Dajka, L. Machura, S. Rogoziński and J. Łuczka, phys. stat. sol (b) 244,  2432 (2007)

\item Magnetic flux in mesoscopic rings: capacity, inertia and kinetics, J. Dajka, S. Rogoziński, Ł. Machura, and J. Łuczka, Acta Physica Polonica B 38,  1737 (2007)

\item Transport of Forced Quantum Motors in the Strong Friction Limit, L. Machura, J. Luczka, P. Talkner and P. Hänggi, Acta Physica Polonica B 38,  1855 (2007)

\item Frequency Windows of Absolute Negative Conductance in Josephson Junctions, L. Machura, M. Kostur, P. Talkner, P. Hänggi, and J. Luczka, AIP Conference Proceedings 922,  455 (2007)

\item Quantum diffusion in biased washboard potentials: strong friction limit, L. Machura, M. Kostur, P. Talkner, J. Luczka and P. Hänggi, Phys. Rev. E 73,  031105 (2006)

\item Forcing inertial Brownian motors: efficiency and negative differential mobility, M. Kostur, L. Machura, P. Hänggi, J. Łuczka and P. Talkner, Physica A 371,  20 (2006)

\item Addendum and Erratum: Optimal strategy for controlling transport in inertial Brownian motion, L. Machura, M. Kostur, F. Marchesoni, P. Talkner, P. Hänggi and J. Luczka, J. Phys.: Condens. Matter 18,  4111-4112 (2006)

\item Statistics of transition times, phase diffusion and synchronization in periodically driven bistable systems, Peter Talkner, Lukasz Machura, Michael Schindler, Peter Hänggi and Jerzy Luczka, New J. Phys. 7,  14 (2005)

\item Optimal strategy for controlling transport in inertial Brownian motion, L. Machura, M. Kostur, F. Marchesoni, P. Talkner, P. Hänggi and J. Luczka, J. Phys.: Condens. Matter 17,  S3741-S3752 (2005)

\item Brownian motors: current fluctuations and rectification effciency, L. Machura, M. Kostur, P. Talkner, J. Luczka, F. Marchesoni and P. Hänggi, Phys. Rev. E 70,  061105 (2004)

\item Consistent Description Of Quantum Brownian Motors Operating At Strong Friction, L. Machura, M. Kostur, P. Hänggi, P. Talkner and J. Luczka, Phys. Rev. E 70,  031107 (2004)

\end{etaremune}